### 2017-11-15 submission/manuscript.tex
change title

\section{The Microbiota and Individual Community Members in Colorectal
Cancer: Is There a Common
Theme?}\label{the-microbiota-and-individual-community-members-in-colorectal-cancer-is-there-a-common-theme}

>>>>

\section{Investigating the Microbiota and Colorectal Cancer: The
Importance of
Community}\label{investigating-the-microbiota-and-colorectal-cancer-the-importance-of-community}
